---
title: "BACS HW (Week8)"
author: "106070038"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

Special thanks to 106002103 for teaching me how to draw a plot by "ggplot2".

# Question 1
## a.What are the means of viewers intentions to share (INTEND.0) for each media type? (report four means)

```{r }
# install.packages('readr')
library(readr)
media1 <- read_csv("pls-media1.csv")
# sapply(media1, mean)
media1_intend0 <- media1$INTEND.0
mean(media1_intend0)

media2 <- read_csv("pls-media2.csv")
# sapply(media2, mean)
media2_intend0 <- media2$INTEND.0
mean(media2_intend0)

media3 <- read_csv("pls-media3.csv")
# sapply(media3, mean)
media3_intend0 <- media3$INTEND.0
mean(media3_intend0)

media4 <- read_csv("pls-media4.csv")
# sapply(media4, mean)
media4_intend0 <- media4$INTEND.0
mean(media4_intend0)
```


## b.Visualize the distribution and mean of intention to share, across all four media.
(Your choice of data visualization; Try to put them all on the same plot and make it look sensible)
```{r }
media1_ <- data.frame(media = rep("media1", length(media1$INTEND.0)), INTEND.0 = media1$INTEND.0)
media2_ <- data.frame(media = rep("media2", length(media2$INTEND.0)), INTEND.0 = media2$INTEND.0)
media3_ <- data.frame(media = rep("media3", length(media3$INTEND.0)), INTEND.0 = media3$INTEND.0)
media4_ <- data.frame(media = rep("media4", length(media4$INTEND.0)), INTEND.0 = media4$INTEND.0)

library(ggplot2)
library(plyr)
media_df <- rbind(media1_, media2_, media3_, media4_)
mu <- ddply(media_df, "media", summarise, grp.mean = mean(INTEND.0))
p <- ggplot(media_df, aes(x=INTEND.0, color = media)) +
            geom_density() + 
            geom_vline(data = mu, aes(xintercept = grp.mean, color = as.factor(media)),
            linetype = "dashed") +
            theme(legend.position = "bottom")
p
```

## c.From the visualization alone, do you feel that media type makes a difference on intention to share?

- Yes, the distribution of media1, media2, media3, media4 look different.

# Question 2  one-way ANOVA
## a.Hnull, Halt
- $Hnull: \mu1 = \mu2 = \mu3 = \mu4$ 
- $Halt: the means are not same$ 

## b. traditional F-statistic

```{r }
media_c <- cbind(media1$INTEND.0, media2$INTEND.0, media3$INTEND.0, media4$INTEND.0)
media_df <- data.frame(media1 = media_c[,1], media2 = media_c[,2], media3 = media_c[,3], media4 = media_c[,4])

n <- nrow(media_df)
sstr <- n*sum((sapply(media_df, mean) - mean(sapply(media_df, mean)))^2) 
df_mstr <- 4-1
mstr <- sstr/df_mstr

sse <- sum((n-1)*sapply(media_df,var)) 
df_mse <- 46*4 - 4
mse <- sse/df_mse

f_value <- mstr/mse
qf(p=0.95, df1=df_mstr, df2=df_mse)
p_value <- pf(f_value, df_mstr, df_mse, lower.tail=FALSE)
```
- sstr = 20.32065, df_mstr = 3, mse = 504.7609, df_mse = 180
- f_value = 2.415479
- qf(p=0.95, df1=df_mstr, df2=df_mse) = 2.654792
- Reject H0.

## c. cut-off values of F for 95% and 99% confidence
```{r }
qf(p=0.95, df1=df_mstr, df2=df_mse)
qf(p=0.99, df1=df_mstr, df2=df_mse)
```

- 95%: 2.654792
- 99%: 3.892266

## d. traditional ANOVA 
```{r }
id1 <- data.frame(strategy=rep(1,length(media1$INTEND.0)), intend=media1$INTEND.0) 
id2 <- data.frame(strategy=rep(2,length(media2$INTEND.0)), intend=media2$INTEND.0) 
id3 <- data.frame(strategy=rep(3,length(media3$INTEND.0)), intend=media3$INTEND.0) 
id4 <- data.frame(strategy=rep(4,length(media4$INTEND.0)), intend=media4$INTEND.0) 
ids <- rbind(id1, id2, id3, id4)
oneway.test(ids$intend ~ ids$strategy, var.equal=TRUE)
```

- One-way analysis of means => F = 2.6167
- 95%: Reject.
- 99%: Not reject.

## e. Do you feel the classic requirements of one-way ANOVA are met?
- classic requirements:
  - 1. Each treatment/population’s response variable is normally distributed => NO
  - 2. The variance (s2) of the response variables is the same for all treatments/populations => NO
  - 3. The observations are independent: the response variables are not related => YES

# Question 3 bootstrapping ANOVA
## a. Bootstrap the null values of F and also the alternative values of the F-statistic
```{r }
boot_anova <- function(t1, t2, t3, t4, treat_nums) { 
  null_grp1 = sample(t1 - mean(t1), replace=TRUE) 
  null_grp2 = sample(t2 - mean(t2), replace=TRUE) 
  null_grp3 = sample(t3 - mean(t3), replace=TRUE) 
  null_grp4 = sample(t4 - mean(t4), replace=TRUE) 
  null_values = c(null_grp1, null_grp2, null_grp3, null_grp4)

    alt_grp1 = sample(t1, replace=TRUE) 
    alt_grp2 = sample(t2, replace=TRUE) 
    alt_grp3 = sample(t3, replace=TRUE) 
    alt_grp4 = sample(t4, replace=TRUE) 

    alt_values = c(alt_grp1, alt_grp2, alt_grp3, alt_grp4)

  c(oneway.test(null_values ~ treat_nums, var.equal=TRUE)$statistic,
    oneway.test(alt_values ~ treat_nums, var.equal=TRUE)$statistic)
}
f_values <- replicate(5000, boot_anova(id1$intend, id2$intend, id3$intend, id4$intend, ids$strategy)) 


f_nulls <- f_values[1,]
f_alts <- f_values[2,]

mean(f_nulls)
quantile(f_nulls, 0.95)
mean(f_alts)
```

## b. the cutoff values for 95% and 99% confidence
```{r }
qf(p=0.95, df1=df_mstr, df2=df_mse)
qf(p=0.99, df1=df_mstr, df2=df_mse)
```

## c. Visualize the distribution of bootstrapped null values of F
```{r }
plot(density(f_nulls), lwd = 2, main = "Density plot of f_nulls") + abline(v = quantile(f_nulls, 0.95), lty="dashed", lwd = 3)
```

## d. According to the bootstrap, do the four types of media produce the same mean intention to share, at 95% confidence? How about at 99% confidence?
- 95%: Reject, the four types of media does not produce the same mean.
- 99%: Not reject, the four types of media produce the same mean.
