---
title: "BACS HW (Week13)"
author: "106070038"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

# Question 1 Let’s visualize how weight and acceleration are related to mpg.
## a. Let’s visualize how weight might moderate the relationship between acceleration and mpg

```{r fig.height = 4, fig.width = 6}
# install.packages("logr")
library(logr)

cars <- read.table("auto-data.txt",)
names(cars) <- c("mpg", "cylinders", "displacement", "horsepower", "weight", "acceleration",
              "model_year","origin", "car_name")

cars_log <- with(cars, data.frame(log(mpg), log(weight), log(acceleration), model_year, origin))

# calculate the mean of log.weight.
mean_log_weight <- mean(cars_log$log.weight.)

# subset cars dataset by mean weight
cars_light <- subset(cars_log, log.weight. < mean_log_weight) 
cars_heavy <- subset(cars_log, log.weight. > mean_log_weight) 

# separate regressions of acceleration vs. mpg by mean weight
acc_regr_light <- lm(log.mpg. ~ log.acceleration., data=cars_light) 
acc_regr_heavy <- lm(log.mpg. ~ log.acceleration., data=cars_heavy) 

# plot the points
with(cars_light, plot(log.acceleration., log.mpg., pch=1, col ="blue", lwd=1,
                      main = "Effect of acceleration on mpg depends on weight of car"))
with(cars_heavy, points(log.acceleration., log.mpg., pch=8, col ="red", lwd=1))

# plot separate regression lines colorized by origin
abline(acc_regr_light, col = "blue", lwd=2, lty=1) 
abline(acc_regr_heavy, col = "red", lwd=2, lty=2) 
```

## b. Report the full summaries of two separate regressions for light and heavy cars where log.mpg. is dependent on log.weight., log.acceleration., model_year and origin

```{r }
regr_light <- lm(log.mpg. ~ ., data = cars_light) 
summary(regr_light)

regr_heavy <- lm(log.mpg. ~ ., data = cars_heavy) 
summary(regr_heavy)
```

## c. (not graded) Using your intuition only: What do you observe about light versus heavy cars so far?

- Answer: <br>
  - heavy car(0.7556) has bigger R-squared than light car(0.7048) <br>
  - the effect of origin in linear model in heavy car is more significant than in light car<br>

# Question 2 Using the fully transformed dataset from above (cars_log), to test whether we have moderation.

## a. (not graded) Between weight and acceleration ability, use your intuition and experience to state which variable might be a moderating versus independent variable, in affecting mileage.

- Answer: I think is **weight**. <br>

## b. Use various regression models to model the possible moderation on log.mpg.:

## i. Report a regression without any interaction terms
```{r }
summary(lm(log.mpg. ~ log.weight. + log.acceleration., data=cars_log))
```

## ii. Report a regression with an interaction between weight and acceleration
```{r }
cor(cars_log$log.weight., cars_log$log.weight.*cars_log$log.acceleration.)
summary(lm(log.mpg. ~ log.weight. + log.acceleration. + log.weight.*log.acceleration., data=cars_log))
```

## iii. Report a regression with a mean-centered interaction term
```{r }
weight_mc <- scale(cars_log$log.weight., center=TRUE, scale=FALSE) 
acceleration_mc <- scale(cars_log$log.acceleration., center=TRUE, scale=FALSE)

cor(weight_mc, weight_mc*acceleration_mc)
summary(lm(log.mpg. ~ weight_mc + acceleration_mc + weight_mc*acceleration_mc, data = cars_log))
```
## iv. Report a regression with an orthogonalized interaction term
```{r }
wei_x_acc <- cars_log$log.weight. * cars_log$log.acceleration.
interaction_regr <- lm(wei_x_acc ~ cars_log$log.weight. + cars_log$log.acceleration.) 
interaction_ortho <- interaction_regr$residuals

round(cor(cbind(cars_log, interaction_ortho)), 2)

summary(lm(log.mpg. ~ cars_log$log.weight. + cars_log$log.acceleration. 
           + interaction_ortho, data = cars_log))
```

## c. For each of the interaction term strategies above (raw, mean-centered, orthogonalized) what is the correlation between that interaction term and the two variables that you multiplied together?
## Raw
```{r }
cor(cars_log$log.weight., cars_log$log.weight.*cars_log$log.acceleration.)
cor(cars_log$log.acceleration., cars_log$log.weight.*cars_log$log.acceleration.)
```
- Answer: **log.weight.** is the moderator. The effect of log.acceleration. is contingent on log.weight..<br>

## Mean-centered
```{r }
cor(acceleration_mc, weight_mc*acceleration_mc)
cor(weight_mc, weight_mc*acceleration_mc)
```
- Answer: Correlation isn't effected by centering. As a result, the correlation is **same as raw**.<br>
  
## Orthogonalized
```{r }
round(cor(cbind(cars_log, interaction_ortho)), 2)
```
- Answer: The correlation between interaction_ortho and log.weight. is 0. And, the correlation between interaction_ortho and log.acceleration. is also 0. <br>
