---
title: "BACS HW (Week 1)"
author: '106070038'
output:
  html_document: default
  PDF: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. What is the 5th element in the original list of ages?
Read table "customers.txt".
```{r }
customers <- read.table("customers.txt", header = TRUE)
```
Find the 5th element.
```{r }
customers[5,1]
```

### 2. What is the fifth lowest age?
Use function **sort()** to order it into ascending or descending order. (Default is ascending.)
```{r }
ages <- sort(customers$age)
ages[5]
```

### 3. Extract the five lowest ages together
Find the five lowest ages.
```{r }
five_lowest_ages <- ages[1:5]
five_lowest_ages
```
### 4. Get the five highest ages by first sorting them in decreasing order first.
Use function **sort()** and add the argument "decreasing = TRUE" to sort it into decreasing.
```{r }
decreasing_ages <- sort(customers$age, decreasing = TRUE)
five_highest_ages <- decreasing_ages[1:5]
five_highest_ages
```
### 5. What is the average (mean) age?
Use function **mean()** to get the arithmetic mean.
```{r }
mean(customers$age)
```
### 6. What is the standard deviation of ages? 
Use function **sd()** to compute the standard deviation of the values.
```{r }
sd(customers$age)
```
### 7. Make a new variable called age_diff, with the difference between each age and the mean age
Use minus sign **-** to subtract mean from each of the values.
```{r }
age_diff <- customers$age - mean(customers$age)
age_diff
```
### 8. What is the average “difference between each age and the mean age”?
The result should be close to zero. Also, **age_diff** can be used to calculate the standard deviation of ages.
```{r }
mean(age_diff)
```
### 9. Visualize the raw data as we did in class: (a) histogram, (b) density plot, (c) boxplot+stripchart
Use function **hist(), plot(), boxplot(), stripchart()** to get each plot. Argument **main** can set the overall title for the plot.
```{r fig.width = 6, fig.height = 4.5}
hist(customers$age, main = "Histogram of ages", xlab = "ages")
plot(density(customers$age), main = "Density plot of ages")
boxplot(customers$age, horizontal = TRUE)
stripchart(customers$age, method = "stack", add = TRUE)
```
