---
title: "BACS HW (Week10)"
author: "106070038"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

# Question 1 Let’s make an automated recommendation system for the PicCollage mobile app.

## a. Let’s explore to see if any sticker bundles seem intuitively similar
i. How many recommendations does each bundle have?<br>
- Answer: **six**(iOS version)<br>

ii. Use your intuition to recommend five other bundles in our dataset that might have similar usage patterns as this bundle. <br>
- Answer: **HeartStickerPack** <br>
-> Similar usage patterns: supersweet, fallinlovewiththefall, hellobaby, valentineStickers, warmncozy(by intuition) <br>
Because all of the stickers above are related to "love"<br>

```{r }
# install.packages("data.table")
library(data.table)
# setwd("/Users/weiwei/Desktop/2021Spring_Courses/BACS/HW8")
ac_bundles_dt <- fread("piccollage_accounts_bundles.csv")
ac_bundles_matrix <- as.matrix(ac_bundles_dt[, -1, with=FALSE])
```

## b. Let’s find similar bundles using geometric models of similarity
i. Let’s create cosine similarity based recommendations for all bundles:
1. Create a matrix or data.frame of the **top 5 recommendations** for all bundles
```{r }
# install.packages("lsa")
# install.packages("SnowballC")
library(SnowballC)
library(lsa)
cos_sim <- cosine(ac_bundles_matrix)
## apply(,1,): by row
cos_sim_add <- apply(cos_sim, 1, mean)
cos_sim_add_rank <- cos_sim_add[order(cos_sim_add, decreasing = TRUE)]
cos_sim_add_rank[1:5]
```
- Answer: springrose, eastersurprise, bemine, watercolor, hipsterholiday<br>

2. Create a new function that automates the above functionality: it should take an accounts-bundles matrix as a parameter, and return a data object with the top 5 recommendations for each bundle in our data set, using cosine similarity.
```{r }
get_top5 <- function (bundle_name,data) {
  reg1 <- data[bundle_name,]
  reg2 <- reg1[order(reg1, decreasing = TRUE)]
  return (reg2[2:6]) ## top1-5, exclude itself(cos_sim==1)
}
```

3. What are the top 5 recommendations for the bundle you chose to explore earlier?

```{r }
get_top5("HeartStickerPack",cos_sim)
```

- Answer: **HeartStickerPack** <br>
-> Similar usage patterns: StickerLite, Emome, WordsStickerPack, HipsterChicSara, BlingStickerPack(by caculation) <br>
Totally not same as what I guess in a-ii.<br>

ii. Let’s create **correlation** based recommendations.
1. Reuse the function you created above (don’t change it; don’t use the cor() function)
2. But this time give the function an accounts-bundles matrix where each 
bundle (column) has already been **mean-centered** in advance.
3. Now what are the top 5 recommendations for the bundle you chose to explore earlier?

```{r }
bundle_means <- apply(ac_bundles_matrix, 2, mean)
bundle_means_matrix <- t(replicate(nrow(ac_bundles_matrix), bundle_means))
ac_bundles_mc_b <- ac_bundles_matrix - bundle_means_matrix
row.names(ac_bundles_mc_b) <- row.names(ac_bundles_dt)
cor_sim_2 <- cosine(ac_bundles_mc_b)
get_top5("HeartStickerPack", cor_sim_2)
class(ac_bundles_mc_b)

```

- Answer: **HeartStickerPack** <br>
-> Similar usage patterns: StickerLite, WordsStickerPack, Emome, BlingStickerPack, HipsterChicSara  <br>
The results are same as (b), however, the order is not same.<br>

iii. Let’s create **adjusted-cosine** based recommendations.
1. Reuse the function you created above (you should not have to change it)
2. But this time give the function an accounts-bundles matrix where each 
account (row) has already been mean-centered in advance.
3. What are the top 5 recommendations for the bundle you chose to explore earlier?

```{r }
#install.packages("data.table")
library(data.table)
library(lsa)
bundle_means <- apply(ac_bundles_matrix, 1, mean)
bundle_means_matrix <- replicate(ncol(ac_bundles_matrix), bundle_means)
ac_bundles_mc_b <- ac_bundles_matrix - bundle_means_matrix
cor_sim_3 <- cosine(ac_bundles_mc_b)
get_top5("HeartStickerPack", cor_sim_3)
```

- Answer: **HeartStickerPack** <br>
-> Similar usage patterns: StickerLite, Emome, BlingStickerPack, HipsterChicSara, WordsStickerPack<br>
The results are same as (b), however, the order is not same.<br>

## c. (not graded) Are the three sets of geometric recommendations similar in nature (theme/keywords) to the recommendations you picked earlier using your intuition alone? What reasons might explain why your computational geometric recommendation models produce different results from your intuition?
- Answer: No, because I just guess it by literal meaning, but we should calculate the similarity. <br>


## d. (not graded) What do you think is the conceptual difference in cosine similarity, correlation, and adjusted-cosine?
- Answer: <br>
  - **Cosine similarity** defined as the angular similarity between two vectors. angle 0 defines match and 90 otherwise. <br>
  - **correlation coefficient** defined as the covariance between two vectors divided by their standard deviations. <br>
  - **adjusted-cosine** is very much similar to pearson similarity except if two are calculated over different set of rated vectors.
