---
title: "BACS HW (Week15)"
author: "106070038"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

Let’s reconsider the security questionnaire from last week, where consumers were asked security related questions about one of the e-commerce websites they had recently used.

# Question 1 Earlier, we examined a dataset from a security survey send to customers of e-commerce websites. However, we only eigenvalue > 1 criteria and the screeplot to find a suitable number of components. Let’s perform a parallel analysis as well this week:

```{r }
# install.packages('readxl')
library('readxl')
security_questions <- read_excel("security_questions.xlsx", sheet = "data")
head(security_questions)
```

## a. Show a single visualization with scree plot of data, scree plot of simulated noise, and a horizontal line showing the eigenvalue = 1 cutoff.

- **visualization with scree plot of data**
```{r fig.height = 4, fig.width = 6}
pca <- prcomp(formula = ~.,  
              data = security_questions,
              scale = TRUE) 
plot(pca, type="line",
     main="Scree Plot for security questions")
```

- **scree plot of simulated noise**
```{r fig.height = 4, fig.width = 6}
set.seed(1)

## Function to run a PCA on n ⨉ p dataframe of random values
sim_noise_ev <- function(n, p) {
  noise <- data.frame(replicate(p, rnorm(n))) 
  return( eigen(cor(noise))$values )
}

## Repeat this k times
evalues_noise <- replicate(100, sim_noise_ev(33, 10))

## Average each of the noise eigenvalues ev over k to produce ev
evalues_mean <- apply(evalues_noise, 1, mean)
dec_pca <- prcomp(security_questions, scale. = TRUE) 
screeplot(dec_pca, type="lines", main="Eigenvalues: security_questions v.s noise") 
lines(evalues_mean, type="blue") 
abline(h=1, lty="dotted")
```

- **a horizontal line showing the eigenvalue = 1 cutoff**
```{r fig.height = 4, fig.width = 6}
plot(pca, type="line",
     main="Scree Plot for security questions")
abline(h=1, col="blue") # Kaiser eigenvalue-greater-than-one rule
```

## b. How many dimensions would you retain if we used Parallel Analysis?
- **Parallel Analysis**: Parallel analyis is an alternative technique that compares the scree of factors of the observed data with that of a random data matrix of the same size as the original. <br>

- Answer: Based on (a), I will retain 2 dimensions.<br>

```{r }
# install.packages("psych")
# library(psych)
# fa.parallel(security_questions,n.obs=NULL,fm="minres",fa="both",nfactors=1, 
# main="Parallel Analysis Scree Plots for security_questions",
# n.iter=20,error.bars=FALSE,se.bars=FALSE,SMC=FALSE,ylabel=NULL,show.legend=TRUE,
# sim=TRUE,quant=.95,cor="cor",use="pairwise",plot=TRUE,correct=.5)
```

# Question 2 Earlier, we examined the eigenvectors of the security dataset. Now, let’s examine factor loadings

## a. Looking at the loadings of the first 3 principal components, to which components does each item seem to best belong?

```{r }
# install.packages("psych")
library(psych)
dec_pca3_orig <- principal(security_questions, nfactor=3, rotate="none", scores=TRUE)
dec_pca3_orig$loadings
```

- Answer: <br>
  - Loadings, which include magnitude and direction are easier to interpret than eigenvectors. lambda > 0.70 is considered a good loading, more than half of item variance explained by PC. <br>
  - As a result, PC1 belongs to Q1, Q14, Q18. <br><br>


## b. How much of the total variance of the security dataset do the first 3 PCs capture?
```{r }
sum(dec_pca3_orig$loadings[,"PC1"]^2) + sum(dec_pca3_orig$loadings[,"PC2"]^2) + sum(dec_pca3_orig$loadings[,"PC3"]^2)
```

## c. Looking at commonality and uniqueness, which items are less than adequately explained by the first 3 principal components?
- Commonality: variance of X100m explained by both principal components <br>
- Uniqueness: Unexplained variance of X100m. u2 = 1 - Communality <br>
- Answer: **Q17** <br>

```{r }
dec_pca3_orig[3]
```

## d. How many measurement items share similar loadings between 2 or more components?
- Answer: <br>
  - Q4 share similar loadings between PC1 and PC2.<br>
  - Q5 share similar loadings between PC1 and PC3.<br>
  - Q12 share similar loadings between PC1 and PC2.<br>
  - Q17 share similar loadings between PC1 and PC2.<br>

## e. Can you distinguish a ‘meaning’ behind the first principal component from the items that load best upon it? (see the wording of the questions of those items)
- Some infomation about site and positive meaning. <br>

# Question 3 To improve interpretability of loadings, let’s rotate the our principal component axes to get rotated components (extract and rotate only three principal components)

## a. Individually, does each rotated component (RC) explain the same, or different, amount of variance than the corresponding principal components (PCs)?
- Answer: All are **different**. <br>
```{r }
dec_pca3_original <- principal(security_questions, nfactor=3, rotate="none", scores=TRUE)
dec_pca3_original$loadings
```

```{r }
dec_pca3_rotate <- principal(security_questions, nfactor=3, rotate="varimax", scores=TRUE)
dec_pca3_rotate$loadings
```


## b. Together, do the three rotated components explain the same, more, or less cumulative variance as the three principal components combined?
- The **same**.

## c. Looking back at the items that shared similar loadings with multiple principal components (#2d), do those items have more clearly differentiated loadings among rotated components?
- Answer: <br>
  - Q4 loadings between PC1 and PC2. -> same <br>
  - Q5 loadings between PC1 and PC3. -> smaller <br>
  - Q12 loadings between PC1 and PC2. -> bigger <br>
  - Q17 loadings between PC1 and PC2. -> bigger <br>


## d. Can you now interpret the “meaning” of the 3 rotated components from the items that load best upon each of them? (see the wording of the questions of those items)
- PC1: some negative word, ex. never, remove, prevent. <br>
- PC2: about "I", "my" and "mine". <br>
- PC3: promise something, ex. make sure and provide me something to protect.

## e. If we reduced the number of extracted and rotated components to 2, does the meaning of our rotated components change?
- Yes, it will definitely change.<br>

```{r }
dec_pca2_rotate <- principal(security_questions, nfactor=2, rotate="varimax", scores=TRUE)
dec_pca2_rotate$loadings
```

## (ungraded) Looking back at all our results and analyses of this dataset (from this week and previous), how many components (1-3) do you believe we should extract and analyze to understand the security dataset? Feel free to suggest different answers for different purposes.
- Answer: **one**, the loading gap between PC1 and PC2 is quite large no matter which approach.
